---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
The following code downloads the source file, unzips and loads the data into variable *stepData*.

```{r, echo = TRUE}
if (!file.exists("activity.zip")) {
  download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip", "activity.zip", method = "curl")
  unzip("activity.zip")
}

stepData <- read.csv("activity.csv", header = TRUE, sep = ",")
stepData$date <- as.Date(stepData$date)
```


## What is mean total number of steps taken per day?

The following code calculates the total number of steps taken per day. The value will be 0 if the data is not available for specific date.

```{r, echo = TRUE}
totalStepsPerDay <- aggregate(stepData$steps, by=list(stepData$date), FUN = sum, na.rm = TRUE)

colnames(totalStepsPerDay) <- c("date", "steps")
totalStepsPerDay

library(ggplot2)
qplot(date, steps, data=totalStepsPerDay, geom="line") + theme(aspect.ratio = 1/4)
```

## What is the average daily activity pattern?

Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r, echo=TRUE}
intervalAverage <- aggregate(steps~date+interval, stepData, mean, na.rm = TRUE)
plot(intervalAverage$interval, intervalAverage$steps, type = "l")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r, echo=TRUE}
intervalAverage[max(intervalAverage$steps),]
```

## Imputing missing values

1) Total number of missing values
```{r, echo=TRUE}
sum(is.na(stepData$steps))
```

2) Fill in all of the missing values in the dataset
```{r, echo=TRUE}
f=function(x){
   x<-as.numeric(x)
   x[is.na(x)]=median(x, na.rm=TRUE) 
   x #display the column
}
# ss=data.frame(apply(stepData,1,f))
```